---
title: "Project 7"
author: "Jeff Boczkaja"
date: "2023-03-01"
output:
  word_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


## House Pricing Data
```{r kc_house_data, echo=FALSE}
kc_house_data <- read.csv("C:/Users/whitl/OneDrive/Desktop/R Files/kc_house_data.csv")

```


-The Minimum house price is `r min(kc_house_data$price)`

-The Maximum house price is `r max(kc_house_data$price)`

-The average house is `r mean(kc_house_data$price)`

-The range of house prices is `r range(kc_house_data$price)`

-The median price of houses is `r median(kc_house_data$price)`

-The standard deviation of house prices is `r sd(kc_house_data$price)`

## Histogram of Prices

```{r histogram, echo=FALSE}
library(ggplot2)
ggplot(data=kc_house_data, aes(x=price))+geom_histogram(bins=30)+ggtitle("Histogram of House Price")+xlab("Price")+ylab("Number")

```


## View and Price Boxplot

```{r boxplot, echo=FALSE}
kc_house_data$view <- as.character(kc_house_data$view)
ggplot(data=kc_house_data, aes(x=view, y=price))+
geom_boxplot(notch=TRUE)
```

## Scatterplot of Price and Sqaure Feet Living

```{r scatterplot, echo=FALSE}
ggplot(kc_house_data, aes(x=price, y=sqft_living)) + geom_point(shape=2) 
```

## First Price Model
```{r Price 1, echo=FALSE}
library(knitr)
Price1 <- lm(price~bedrooms+bathrooms+sqft_living, data=kc_house_data)
my.table = as.data.frame(Price1$coefficients)
kable(my.table, caption = 'Price 1 Model')
```
The adjusted r squared for model 1 is `r summary(Price1)$adj.r.squared`

## Second Price Model
```{r price2, echo=FALSE}
library(knitr)
Price2 <- lm(price~bedrooms*bathrooms*sqft_living, data=kc_house_data)
my.table = as.data.frame(Price2$coefficients)
kable(my.table, caption = 'Price Model 2')
```
The adjusted r squared for model 2 is `r summary(Price2)$adj.r.squared`

## Third Price Model
```{r price3, echo=FALSE}
library(knitr)
kc_house_data$waterfront <- as.factor(kc_house_data$waterfront)
kc_house_data$grade <- as.factor(kc_house_data$grade)
Price3 <- lm(price~bedrooms+bathrooms+sqft_living+waterfront+grade, data=kc_house_data)
my.table = as.data.frame(Price3$coefficients)
kable(my.table, caption = 'Price Model 3')
```
The adjusted r squared for model 3 is `r summary(Price3)$adj.r.squared`

### We would reccomend the third price model.


